Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-09-29 ms.tex
Updates from Overleaf

@@

\begin{figure}[ht!]
%
%\includegraphics{}  % preferably .eps
\caption{Pixels lost as a function of satellite dodging weight. \label{fig-pixel-loss-weight}}
\end{figure}

>>>>

XXX--I'll add some text describing the baseline scheduler that we use--note that we only run for the first year. Maybe add a zonodo to the repo so we can cite where we got the baseline simulation from.

@@

\begin{figure}[ht!]
\plottwo{plots/streaklen_v_weight.pdf}{plots/streakfrac_v_weight.pdf}
\plottwo{plots/nexp_v_weight.pdf}{plots/streak_length_v_deltam.pdf}
\caption{Results from simulating the first year of Rubin observations in the presence of different satellite constellations and varying how strongly the scheduler attempts to avoid satellites.  Top panels show that, as expected, the number of streaks and mean streak length decrease as more emphasis is put on satellite dodging. Bottom panels show the resulting trade off, as avoiding satellites forces the scheduler to make longer slews and observe less desirable parts of the sky, resulting in fewer total exposures in the first year and a shallower median coadded depth. \label{fig-pixel-loss-weight}}
\end{figure}
